---
title: "RiA_chap02"
author: "Artifex"
date: "2016-1-15"
output: pdf_document
---

## Create a Dataset

### 1. Understanding datasets
1. Data structure:
  - scalar, vector, array, data frame, list
  - 存储数据的工具，类似于碗、盘子、碟子，是一个容器

2. Data type(mode):
  - numeric, character, logical, complex, raw(bytes)
  - 数据，类似于米饭、菜、花生米，是容器内的东西
  
### 2. Data Structures
1. Vector
  - **One-dimensional** array that holds **single mode** of data.
  - Use c() to create a vector.
  - Select the elements in a vetor.
```{r}
a <- c(1, -2, 3, -4, 5, -6)
a[2] # use a scalar to select the element
a[c(1, 2, 4)]  # use a numeric vector to select the elements
```

2. Matrix
  - **Two-dimensional** array that holds **single mode** of data.
  - Use matrix() function to create a vector.
  - Select the elements in a matrix.
```{r}
x <- matrix(1:24, nrow=6)
x
y <- matrix(1:24, nrow=6, byrow=TRUE) # byrow=FALSE by default
y

cells <- c(1,26,24,68)
rnames <- c("R1", "R2")
cnames <- c("C1", "C2")
mymatrix <- matrix(cells, nrow=2, ncol=2, byrow=TRUE, 
                   dimnames=list(rnames, cnames))
mymatrix
# retrieve data from a matrix
x[2, ] # the entire 2nd row
x[, 3] # the entire 3rd col
x[2, 3] # the element at 2rd row, 3rd col
x[c(2:4), c(1:3)] # a sub matrix
```

3. Array

